Aircraft Wildlife Collisions

### 2021-07-20 draft_final.Rmd
Minor corrections

factor_ac_mass <- c("<=2250 kg", "2251-5700 kg", "5701-27000 kg", "27001-272000 kg", ">272000 kg")
birds$ac_mass <- as.factor(birds$ac_mass)#, levels=factor_ac_mass)
birds$ac_mass_names <- revalue(as.factor(birds$ac_mass),     c("1"="<2250",        "2"="2251-5700",        "3"="5701-27000",        "4"="27001-272000",       "5"=">272000"))
birds$num_engs <- as.factor(birds$num_engs)

@@

@@

```{r echo=FALSE, message=FALSE, fig.asp=0.5}
#get rows where birds struck is missing
df <- birds[is.na(birds$birds_struck), 
            c("remarks", "birds_seen", "effect", "birds_struck")]
no_strike <- grepl("NOT A STRIKE|NO STRIKE|NOT A STRKE", df$remarks)
# set birds_struck to 0 for "no strike"
birds[is.na(birds$birds_struck),][no_strike,"birds_struck"] <- "0"

@@

machines <- birds[!is.na(birds$height) & !is.na(birds$speed),] %>%
  group_by(atype) %>%
  summarise(max_speed = max(speed),
            max_height = max(height),
            num_engs = median(as.integer(num_engs)),
            ac_mass = median(as.integer(ac_mass)),
            ac_mass_names = median(as.integer(ac_mass_names)))

@@

machines$num_engs <- factor(machines$num_engs, levels=1:4)
machines$ac_mass <- factor(machines$ac_mass, levels=1:5)
machines$ac_mass_names <- factor(machines$ac_mass_names)

machines$ac_mass2 <- ifelse(as.integer(machines$ac_mass)<3,1,ifelse(as.integer(machines$ac_mass)==3,2,3))
machines$ac_mass2 <- factor(machines$ac_mass2, levels=1:3)

top10_aircrafts_bar <- machines %>%
arrange(desc(n)) %>%
head(10) %>%
ggplot(aes(x=reorder(atype, n), y=n, fill = ac_mass))+
  geom_bar(stat="identity") +
  theme(legend.position="none") +
  labs(title= "Top 10 frequent strikes by aircraft", x="aircraft model") +
  coord_flip()

set.seed(43)
top50 <- machines[order(-machines$n)[1:50],] %>% 
  mutate(angle = 30 * sample(-2:2, n(), replace = TRUE, prob = c(1, 1, 4, 1, 1)))
top50_aircrafts_wordcloud <- ggplot(top50) +
  aes(label = atype, size=n, color=ac_mass)+#, angle=angle) +
  geom_text_wordcloud_area(
    #mask = png::readPNG(source="flugzeug6-3.png"),
    #mask = png::readPNG(source="/Users/Vy/Documents/flugzeug6-3.png"),
    rm_outside = TRUE) +
  scale_size_area(max_size = 3) +
  scale_color_brewer(palette="BuPu") +
  #ggtitle("top 50 aircraft models causing strikes")
  #theme(plot.title = element_text(vjust=-20)) +
  theme.title+
  labs(
    title="Top 50 aircrafts involved in collisions",
    subtitle = "Model types by number of collisions"
       )

aircraft_speed_height <- ggplot(top50[!is.na(top50$ac_mass),]) +
#aircraft_speed_height <- ggplot(machines[!is.na(machines$ac_mass),]) +
  aes(x=max_speed, y=max_height, color = ac_mass) +
  geom_point() +
  geom_smooth(method = lm, aes(x=max_speed, y = max_height, group = "black", fill = "black", ), se = FALSE) +
  theme(legend.position="right") +
  scale_color_brewer(palette="BuPu") +
  guides(fill = FALSE)+
  theme.title+
  labs(
    subtitle = "max speed vs. max height"
  )

@@

```{r echo=FALSE, fig.asp=0.5}
machines_c <- machines[complete.cases(machines),]
p <- ggplot(machines[!is.na(machines$num_engs) & !is.na(machines$ac_mass),]) +
  aes(x=max_speed, y=max_height, color = ac_mass) +
  geom_point() +
  scale_color_brewer(palette="BuPu") +
  theme(plot.title = element_text(
      hjust = 0, 
      size = 12,
      color = "#016c59",
      face = "bold"
    ),
    plot.subtitle = element_text(
      hjust = 0, 
      size = 10,
      color = "gray50",
      face = "italic"
    ),
    strip.background = element_rect(colour = "black", fill = "white"),
    panel.background = element_rect(colour = "grey50")) +
  labs(
    title = "All aircraft models",
    subtitle = "max speed vs. max height by number of engines"
  )

@@

birds_strike_ac_mass <- ggplot(birds_struck_minorities)+
aes(x=ac_mass, fill=birds_struck)+
  #scale_fill_manual(values=c("#eff3ff", "#3182bd", "#08519c")) +
  scale_fill_manual(values=brewer.pal(6,"Blues")[c(1,4,5)]) +
  geom_bar(position = "fill") +
  geom_text(aes(label=ifelse(round(..count../ac_struck_sums[1:14],2) > 0.1,round(..count../ac_struck_sums[1:14],2) , "")),
            stat='count',
            size = 2.3,
            position=position_fill(vjust = 0.5))+
  theme.title+
  labs(subtitle = "Birds struck (subset) by aircraft mass")

@@

```{r echo=FALSE, fig.asp=0.5}
#Create new column
#calculate only when seen is not na
seen_vs_strike <- birds[birds$birds_seen!="None" & !is.na(birds$birds_struck),]
seen_vs_strike$birds_struck <- factor(seen_vs_strike$birds_struck)
seen_vs_strike$birds_seen <- factor(seen_vs_strike$birds_seen)
seen_vs_strike$less_strike_than_seen <- as.factor(as.integer(seen_vs_strike$birds_struck) < as.integer(seen_vs_strike$birds_seen)+2)

@@

# phase of flight by birdsstruck < birds seen
seen_vs_strike_phase <- ggplot(seen_vs_strike[!is.na(seen_vs_strike$phase_of_flt) & as.integer(seen_vs_strike$phase_of_flt)>2,]) +
  aes(x=phase_of_flt, fill=less_strike_than_seen) +
  scale_fill_manual(values = color_pal_TF) +
  geom_bar(position = "fill") +
 # geom_text(aes(label=..count..),
 # geom_text(aes(label=ifelse(round(..count../less_strike_sums[2:16],2) >
  geom_text(aes(label=ifelse(round(..count../less_strike_sums,2) >
  #0.1,round(..count../less_strike_sums[2:16],2) , "")),
                               0.1,round(..count../less_strike_sums,2) , "")),
            stat='count',
            size = 3,
            position=position_fill(vjust = 0.5))+
  coord_flip() +
  theme(legend.position="right", axis.title.y = element_blank())+
  theme.title+
  labs(title="Variables influencing less strikes than seen",
       subtitle = "Proportion of less strike than seen \nby phase of flight",
       fill='less strike \nthan seen'
       )

#ac_mass by leess-strike-than-seen (MOSAIC)
seen_vs_strike_ac_mass <- ggplot(seen_vs_strike[!is.na(seen_vs_strike$ac_mass),]) +
  geom_mosaic(aes(x=product(ac_mass), fill=less_strike_than_seen)) +
  scale_fill_manual(values = color_pal_TF)+
  theme(legend.position="none", axis.text.y=element_blank(), axis.ticks.y = element_blank())+
  ylab("")

#num_engs by leess-strike-than-seen (MOSAIC)
seen_vs_strike_num_engs <- ggplot(seen_vs_strike[!is.na(seen_vs_strike$num_engs),]) +
  geom_mosaic(aes(x=product(num_engs), fill=less_strike_than_seen)) +
  scale_fill_manual(values = color_pal_TF)+
  theme(legend.position="none", axis.text.y=element_blank(),axis.ticks.y = element_blank())+
  ylab("")

seen_vs_strike_phase + seen_vs_strike_ac_mass / seen_vs_strike_num_engs
```

@@

#mosaic plot better than barplot visualizes also absolute differences
birds_effect_acmass <- ggplot(birds[!is.na(birds$ac_mass) & !is.na(birds$effect),]) +
  geom_mosaic(aes(x = product(ac_mass), fill=effect)) +
  scale_fill_brewer(palette="OrRd") +
  theme(legend.position="none", 
        axis.text.y=element_blank(), 
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) +
  theme.title+
  labs(subtitle = "Effect by aircraft mass")

#birdds_seenYes by effect
birds_effect_seenYes <- ggplot(birds[!is.na(birds$effect),]) +
  geom_mosaic(aes(x = product(birds_seenYes), fill=effect))+
  scale_fill_brewer(palette="OrRd") +
  #theme(legend.title = element_blank())
  theme(legend.position="none", 
        axis.text.y=element_blank(), 
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) +
  theme.title+
  labs(xlab= "birds seen?", subtitle = "Effect by birds seen or not")

@@

``` {r echo=FALSE}
# Number of collisions per state
state_plot_df<-birds[birds$birds_struck != "0" & !is.na(birds$birds_struck) & !is.na(birds$state) & !is.na(birds$ac_mass),]
state_plot_df$ac_mass_renamed<-revalue(as.factor(state_plot_df$ac_mass), 
     c("1"="2250 kg or less", "2"="2251-5700 kg", "3"="5701-27000 kg", "4"="27001-272000 kg", "5"="above 272000 kg"))
state_plot<-ggplot(data = state_plot_df) +
  aes(y = fct_rev(fct_infreq(state)), fill = ac_mass_renamed) + 
  guides(fill=guide_legend(title="Mass of the aircraft")) + 
  scale_fill_brewer(palette="Purples") +
  geom_bar() + 
  labs(title="Number of collisions by State",
       subtitle="Divided by the mass of the aircraft",
       x = "Number of Collisions",
       y = "U.S State") +
  theme.title + 
  theme(legend.position="right") +
  scale_y_discrete(breaks=every_nth(3))

@@

## Birds/Non-Birds in two maps next to each other
map.bird<-ggplot(state.coll.bird.nonbird, aes(map_id = state)) +
  geom_map(aes(fill = bird), map = us.state) +
  scale_fill_distiller(palette = "PuBu", trans="reverse") +
  guides(fill=guide_colorbar(title="No. of collisions")) + 
  expand_limits(x = us.state$long, y = us.state$lat) +
  labs(x = "Longitude", y = "Latitude") +
  theme.title +
  theme(legend.position="bottom") +
   theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank()) +
  theme(plot.margin=unit(c(5.5,20,5.5,5.5),"points")) +
  coord_fixed(1.3)

map.non.bird<-ggplot(state.coll.bird.nonbird, aes(map_id = state)) +
  geom_map(aes(fill = nonbird), map = us.state) +
  scale_fill_distiller(palette = "PuBu", trans="reverse") +
  guides(fill=guide_colorbar(title="No. of collisions")) + 
  expand_limits(x = us.state$long, y = us.state$lat) +
  labs(x = "Longitude", y = "") +
  theme.title +
  theme(legend.position="bottom") +
  theme(axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank(),
        axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank()) +
  theme(plot.margin=unit(c(5.5,5.5,5.5,20),"points")) +
  coord_fixed(1.3)

@@

```{r echo=FALSE}
birds.filt<-birds[!is.na(birds$birds_struck),]

@@

# Time of Day
tod_plot<-ggplot(birds.filt[!is.na(birds.filt$time_of_day),]) +
  aes(x = month, fill=time_of_day) +
  scale_fill_manual(values = color_pal_TOD) +
  labs(x = "Month", y = "Prop. number of collisions") +
  guides(fill=guide_legend(title="Time of Day")) +
  geom_bar(position="fill") +
  scale_x_discrete(labels=xlabels)
```
```{r echo=FALSE, fig.asp=0.5}
(sky_month_plot + tod_plot)
```

@@

```{r echo=FALSE, fig.asp=1.0}
(month_plot / woy_plot) / (week_plot + half.year.plot)
```

@@

```{r echo=FALSE, fig.asp=0.8}
birds$struck_num<-unclass(birds$birds_struck)
birds$struck_num <- mapvalues(birds$struck_num, 
                                     from=c(1,2,3,4,5), 
                                     to=c(0,1,5,50,100))

@@

```{r echo=FALSE, fig.asp=1.0}
birds.with.statenames<-merge(x = birds.filtered.struck.num, y = df.state, by.x = "state", by.y = "state.abb")

>>>>

#factor_ac_mass <- c("<=2250 kg", "2251-5700 kg", "5701-27000 kg", "27001-272000 kg", ">272000 kg")
#birds$ac_mass <- as.factor(birds$ac_mass)#, levels=factor_ac_mass)
#birds$ac_mass_names <- revalue(as.factor(birds$ac_mass),     c("1"="<2250",        "2"="2251-5700",        "3"="5701-27000",        "4"="27001-272000",       "5"=">272000"))

ac_mass_names<- c("1"="< 2.25 t", "2"="2.25-5.7 t", "3"="5.7-27 t", "4"="27-272 t", "5"="> 272 t")
birds$ac_mass_renamed<-revalue(as.factor(birds$ac_mass), ac_mass_names)

birds$num_engs <- as.factor(birds$num_engs)

@@

# Introduction

In this paper we want to investigate a dataset of aircraft-wildlife collisions in the U.S. in the 90s. We start by introducing the data and some steps we took regarding data preparation.
For our analysis we then first take a look at what kind of aircrafts are frequently involved in bird/wildlife strikes. After that we examine what kind of circumstances lead to such collisions and if there are any dependencies between certain variables.
In the following chapter we then also take location into account to analyze if this has any influence on the kind of wildlife involved in the collisions.
For the last research topic we focus on the time variable and put that in relation to the previous results.

We then finish with a summary of our findings and further research questions that could possibly be further analyzed in the future.

@@

```{r echo=FALSE, message=FALSE, fig.asp=0.4}
#get rows where birds struck is missing
df <- birds[is.na(birds$birds_struck), 
            c("remarks", "birds_seen", "effect", "birds_struck")]
no_strike <- grepl("NOT A STRIKE|NO STRIKE|NOT A STRKE", df$remarks)
# set birds_struck to 0 for "no strike"
birds[is.na(birds$birds_struck),][no_strike,"birds_struck"] <- "0"

@@

machines <- birds[!is.na(birds$height) & !is.na(birds$speed),] %>%
  group_by(atype) %>%
  summarise(max_speed = max(speed),
            max_height = max(height),
            num_engs = median(as.integer(num_engs)),
            ac_mass = median(as.integer(ac_mass)),
            ac_mass_renamed = median(as.integer(ac_mass_renamed)))

@@

machines$num_engs <- factor(machines$num_engs, levels=1:4)
machines$ac_mass <- factor(machines$ac_mass, levels=1:5)
machines$ac_mass_renamed <- revalue(factor(machines$ac_mass_renamed, levels=1:5), ac_mass_names)

set.seed(43)
top50 <- machines[order(-machines$n)[1:50],] %>% 
  mutate(angle = 30 * sample(-2:2, n(), replace = TRUE, prob = c(1, 1, 4, 1, 1)))
top50_aircrafts_wordcloud <- ggplot(top50) +
  aes(label = atype, size=n, color=ac_mass)+#, angle=angle) +
  geom_text_wordcloud_area(
    mask = png::readPNG(source="flugzeug6-3.png"),
    #mask = png::readPNG(source="/Users/Vy/Documents/R_Projects/Data_Visualization/flugzeug6-3.png"),
    rm_outside = TRUE) +
  scale_size_area(max_size = 3) +
  scale_color_brewer(palette="BuPu") +
  #ggtitle("top 50 aircraft models causing strikes")
  #theme(plot.title = element_text(vjust=-20)) +
  theme.title+
  labs(
    title="Top 50 aircrafts involved in collisions",
    subtitle = "Model types by number of collisions"
       )

aircraft_speed_height <- ggplot(top50[!is.na(top50$ac_mass),]) +
#aircraft_speed_height <- ggplot(machines[!is.na(machines$ac_mass),]) +
  aes(x=max_speed, y=max_height, color = ac_mass_renamed) +
  geom_point() +
  geom_smooth(method = lm, aes(x=max_speed, y = max_height, group = "black", fill = "black", ), se = FALSE) +
  theme(legend.position="right") +
  scale_color_brewer(name="ac_mass in tons", palette="BuPu") +
  guides(fill = FALSE)+
  theme.title+
  labs(
    subtitle = "max speed vs. max height"
  )

@@

```{r echo=FALSE, fig.asp=0.5}
p <- ggplot(machines[!is.na(machines$num_engs) & !is.na(machines$ac_mass),]) +
  aes(x=max_speed, y=max_height, color = ac_mass_renamed) +
  geom_point() +
  scale_color_brewer(name="ac_mass in tons", palette="BuPu") +
  theme(plot.title = element_text(
      hjust = 0, 
      size = 12,
      color = "#016c59",
      face = "bold"
    ),
    plot.subtitle = element_text(
      hjust = 0, 
      size = 10,
      color = "gray50",
      face = "italic"
    ),
    strip.background = element_rect(colour = "black", fill = "white"),
    panel.background = element_rect(colour = "grey50")) +
  labs(
    title = "All aircraft models",
    subtitle = "max speed vs. max height by number of engines"
  )

@@

birds_strike_ac_mass <- ggplot(birds_struck_minorities)+
aes(x=ac_mass_renamed, fill=birds_struck)+
  #scale_fill_manual(values=c("#eff3ff", "#3182bd", "#08519c")) +
  scale_fill_manual(values=brewer.pal(6,"Blues")[c(1,4,5)]) +
  geom_bar(position = "fill") +
  geom_text(aes(label=ifelse(round(..count../ac_struck_sums[1:14],2) > 0.1,round(..count../ac_struck_sums[1:14],2) , "")),
            stat='count',
            size = 2.3,
            position=position_fill(vjust = 0.5))+
  theme.title+
  labs(subtitle = "Birds struck (subset) by aircraft mass") + 
  xlab("ac_mass in tons") + 
  theme(axis.text.x = element_text(angle = 90))

@@

```{r echo=FALSE, fig.asp=0.3}
#Create new column
#calculate only when seen is not na
seen_vs_strike <- birds[birds$birds_seen!="None" & !is.na(birds$birds_struck),]
seen_vs_strike$birds_struck <- factor(seen_vs_strike$birds_struck)
seen_vs_strike$birds_seen <- factor(seen_vs_strike$birds_seen)
seen_vs_strike$less_strike_than_seen <- as.factor(as.integer(seen_vs_strike$birds_struck) < as.integer(seen_vs_strike$birds_seen)+2)

@@

# phase of flight by birdsstruck < birds seen
seen_vs_strike_phase <- ggplot(seen_vs_strike[!is.na(seen_vs_strike$phase_of_flt) & as.integer(seen_vs_strike$phase_of_flt)>2,]) +
  aes(x=phase_of_flt, fill=less_strike_than_seen) +
  scale_fill_manual(values = color_pal_TF) +
  geom_bar(position = "fill") +
 # geom_text(aes(label=..count..),
 # geom_text(aes(label=ifelse(round(..count../less_strike_sums[2:16],2) >
  geom_text(aes(label=ifelse(round(..count../less_strike_sums,2) >
  #0.1,round(..count../less_strike_sums[2:16],2) , "")),
                               0.1,round(..count../less_strike_sums,2) , "")),
            stat='count',
            size = 3,
            position=position_fill(vjust = 0.5))+
  #coord_flip() +
  theme(legend.position="right", axis.title.y = element_blank())+
  theme.title+
  labs(title="Variables influencing less strikes than seen",
       subtitle = "Proportion of less strike than seen \nby phase of flight",
       fill='less strike \nthan seen'
       )

#ac_mass by less-strike-than-seen (MOSAIC)
seen_vs_strike_ac_mass <- ggplot(seen_vs_strike[!is.na(seen_vs_strike$ac_mass),]) +
  geom_mosaic(aes(x=product(ac_mass_renamed), fill=less_strike_than_seen)) +
  scale_fill_manual(values = color_pal_TF)+
  theme(legend.position="none", axis.text.y=element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_text(angle = 90))+
  ylab("") + xlab("ac_mass in tons")

#num_engs by less-strike-than-seen (MOSAIC)
seen_vs_strike_num_engs <- ggplot(seen_vs_strike[!is.na(seen_vs_strike$num_engs),]) +
  geom_mosaic(aes(x=product(num_engs), fill=less_strike_than_seen)) +
  scale_fill_manual(values = color_pal_TF)+
  theme(legend.position="none", axis.text.y=element_blank(),axis.ticks.y = element_blank())+
  ylab("")

seen_vs_strike_phase
```
```{r echo=FALSE, fig.asp=0.35}
seen_vs_strike_ac_mass + seen_vs_strike_num_engs
```

@@

#mosaic plot better than barplot visualizes also absolute differences
birds_effect_acmass <- ggplot(birds[!is.na(birds$ac_mass_renamed) & !is.na(birds$effect),]) +
  geom_mosaic(aes(x = product(ac_mass_renamed), fill=effect)) +
  scale_fill_brewer(palette="OrRd") +
  theme(legend.position="none", 
        axis.text.y=element_blank(), 
        axis.text.x = element_text(angle =90),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) +
  theme.title+
  labs(subtitle = "Effect by aircraft mass") +
  xlab("ac_mass in tons")

#birdds_seenYes by effect
birds_effect_seenYes <- ggplot(birds[!is.na(birds$effect),]) +
  geom_mosaic(aes(x = product(birds_seenYes), fill=effect))+
  scale_fill_brewer(palette="OrRd") +
  #theme(legend.title = element_blank())
  theme(legend.position="none", 
        axis.text.y=element_blank(), 
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) +
  theme.title+
  labs(subtitle = "Effect by birds seen or not") +
  xlab("birds_seen = YES")

@@

``` {r echo=FALSE}
# Number of collisions per state
state_plot_df<-birds[birds$birds_struck != "0" & !is.na(birds$birds_struck) & !is.na(birds$state) & !is.na(birds$ac_mass_renamed),]
#state_plot_df$ac_mass_renamed<-revalue(as.factor(state_plot_df$ac_mass), 
     #c("1"="2250 kg or less", "2"="2251-5700 kg", "3"="5701-27000 kg", "4"="27001-272000 kg", "5"="above 272000 kg"))
state_plot<-ggplot(data = state_plot_df) +
  aes(y = fct_rev(fct_infreq(state)), fill = ac_mass_renamed) + 
  guides(fill=guide_legend(title="Mass of aircraft in tons")) + 
  scale_fill_brewer(palette="Purples") +
  geom_bar() + 
  labs(title="Number of collisions by State",
       subtitle="Divided by the mass of the aircraft",
       x = "Number of Collisions",
       y = "U.S State") +
  theme.title + 
  theme(legend.position="right") +
  scale_y_discrete(breaks=every_nth(3))

@@

## Birds/Non-Birds in two maps next to each other
map.bird<-ggplot(state.coll.bird.nonbird, aes(map_id = state)) +
  geom_map(aes(fill = bird), map = us.state) +
  scale_fill_distiller(palette = "PuBu", trans="reverse") +
  guides(fill=guide_colorbar(title="No. of collisions")) + 
  expand_limits(x = us.state$long, y = us.state$lat) +
  labs(x = "Longitude", y = "Latitude") +
  theme.title +
  theme(legend.position="bottom") +
   theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) +
  theme(plot.margin=unit(c(5.5,20,5.5,5.5),"points")) +
  coord_fixed(1.3)

map.non.bird<-ggplot(state.coll.bird.nonbird, aes(map_id = state)) +
  geom_map(aes(fill = nonbird), map = us.state) +
  scale_fill_distiller(palette = "PuBu", trans="reverse") +
  guides(fill=guide_colorbar(title="No. of collisions")) + 
  expand_limits(x = us.state$long, y = us.state$lat) +
  labs(x = "Longitude", y = "") +
  theme.title +
  theme(legend.position="bottom") +
  theme(axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank(),
        axis.text.x=element_blank(), axis.ticks.x=element_blank()) +
  theme(plot.margin=unit(c(5.5,5.5,5.5,20),"points")) +
  coord_fixed(1.3)

@@

```{r echo=FALSE, warning=FALSE, message=FALSE, }
birds.filt<-birds[!is.na(birds$birds_struck),]

@@

# Time of Day
tod_plot<-ggplot(birds.filt[!is.na(birds.filt$time_of_day),]) +
  aes(x = month, fill=time_of_day) +
  scale_fill_manual(values = color_pal_TOD) +
  labs(x = "Month", y = "Prop. number of collisions") +
  guides(fill=guide_legend(title="Time of Day")) +
  geom_bar(position="fill") +
  scale_x_discrete(labels=xlabels)
```
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.asp=0.5}
(sky_month_plot + tod_plot)
```

@@

```{r echo=FALSE, warning=FALSE, message=FALSE, fig.asp=1.0}
(month_plot / woy_plot) / (week_plot + half.year.plot)
```

@@

```{r echo=FALSE, warning=FALSE, message=FALSE, fig.asp=0.8}
birds$struck_num<-unclass(birds$birds_struck)
birds$struck_num <- mapvalues(birds$struck_num, 
                                     from=c(1,2,3,4,5), 
                                     to=c(0,1,5,50,100))

@@

```{r echo=FALSE, warning=FALSE, message=FALSE, fig.asp=1.0}
birds.with.statenames<-merge(x = birds.filtered.struck.num, y = df.state, by.x = "state", by.y = "state.abb")
